---
title: "p8105_hw6_xy2397"
author: "Xue Yang"
date: "11/20/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))

set.seed(1)
```


## Problem 1

**Load and clean the data**
```{r, message = FALSE}
# load the data
homicide = read_csv(file = "./data/homicide-data.csv") 
```

```{r}
homicide = 
  homicide %>% 
  # create a city_state variabl
  unite(city_state, city, state, sep = ",") %>% 
  # create a binary variable which "0" indicates homicide is unsolved, "1" solved
  mutate(resolved = as.numeric(disposition == "Closed by arrest"))  

homicide_df = 
  homicide %>%
  mutate(city_state = as.factor(city_state)) %>% 
  # omit some cities
  filter(!(city_state %in% c("Dallas,TX", "Phoenix,AZ", "Kansas City,MO", "Tulsa,AL"))) %>% 
  # modify victim_race to have categories white and non-white, with white as the reference category
  # include the "unknown" victim_race to be non-white category
  mutate(victim_race = ifelse(victim_race == "White", "white", "non-white"),
         victim_race = as.factor(victim_race),
         victim_race = relevel(victim_race, ref = "white")) %>% 
  # change victim_age to numeric, and omit the NA
  mutate(victim_age = as.numeric(victim_age)) %>% 
  filter(!is.na(victim_age))

```

**Fit the logistic regression model**

For city "Baltimore, MD", fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors.

Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.
```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore,MD") %>% 
  select(resolved, victim_race, victim_age, victim_sex)

fit = glm(resolved ~ victim_age + victim_sex + victim_race,
          data = baltimore_df,
          family = binomial)

fit %>% 
  broom::tidy() %>% 
  mutate(aOR = exp(estimate),
         conf_low = exp(confint(fit, level = 0.95))[,1],
         conf_high = exp(confint(fit, level = 0.95))[,2]) %>% 
  knitr::kable(digits = 3)
```

From the results, we know that the aOR = exp(estimate) for victim_racenon-white indicates the differences non-white victims to white victims of adjusted odds ratio for solving homicides, keeping all the other variables fixed. 

In this way, we can filter the term to "victim_racenon-white" to get our results:

```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(aOR = exp(estimate),
         conf_low = exp(confint(fit, level = 0.95))[,1],
         conf_high = exp(confint(fit, level = 0.95))[,2]) %>% 
  filter(term == "victim_racenon-white") %>% 
  mutate(city_state = "Baltimore,MD") %>% 
  select(city_state, aOR, conf_low, conf_high) %>% 
  knitr::kable(digits = 3)
```

The above is the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed for the city of "Baltimore, MD".


Now run glm for each of the cities in the dataset.

```{r}
# create a function of city to gain the aOR and confidence interval 
logistic_fit = function(city){
  
  city_data = 
    homicide_df %>% 
    filter(city_state == city) %>% 
    select(resolved, victim_race, victim_age, victim_sex)

  
  fit = 
    glm(resolved ~ victim_age + victim_sex + victim_race, 
        data = city_data, 
        family = binomial) 
    
  
  result = 
    fit %>%
    broom::tidy() %>% 
    mutate(aOR = exp(estimate),
           conf_low = exp(confint(fit, level = 0.95))[,1],
           conf_high = exp(confint(fit, level = 0.95))[,2]) %>% 
    filter(term == "victim_racenon-white") 
  
  result
  
}

```

```{r, message = FALSE, warning = FALSE}

# identify city
city = 
  homicide_df %>% 
  count(city_state) %>% 
  unnest()

# use the function created above to calculate for each city
output = 
  tibble(city = city$city_state) %>% 
  mutate(estimates = purrr::map(.x = city, ~logistic_fit(city = .x))) %>%
  unnest() %>% 
  select(-term)

# tidy the output
output %>% 
  select(city, aOR, conf_low, conf_high) %>% 
  knitr::kable(digits = 3)

```


In the table above, we gain a dataframe with estimated ORs and CIs for each city.

**Create a plot**

Create a plot shows the estimated aORs and CIs for each city. 
```{r}
output %>% 
  # organize cities according to estimated aOR
  mutate(city = forcats::fct_reorder(city, aOR)) %>% 
  ggplot(aes(x = city, y = aOR, color = city)) +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  labs(
    title = "aORs and CIs for City",
    x = "City",
    y = "aORs and CIs"
  ) +
  viridis::scale_color_viridis(
    name = "City",
    discrete = TRUE
  ) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

From the plot, we can find that city "Boston, MA" has the lowest adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed, while "Tampa, FL" has the highest.

And for more than a half city, aOR<1, which means that the odds of solving homicides in "non-white" victims is less than the odds in "white" victim.

## Problem 2

**Load and clean the data**
```{r}
birthweight = read_csv(file = "./data/birthweight.csv") 
```

Firstly, we change variables "babysex", "frace", "malform" and "mrace" into factor variables.
```{r}
# change some varibles from numeric to factors
birthweight_df =
  birthweight %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))  
```

Then by checking for the missing data, we find that there is no missing data in the dataset.
```{r}
# check for missing data
table(is.na(birthweight_df))
```

**Exploration of the data**

We look at the distribution of our outcome baby’s birth weight: "bwt", from the plot we can find that the distribution of "bwt" is not significant skewed, so we can assume the normality of it.

```{r}
birthweight_df %>% 
  ggplot(aes(x = bwt)) +
  geom_histogram() +
  labs(
    title = "Histogram of Birth Weight",
    x = "Birth Weight",
    y = "Frequency"
  )
```

Then we focus on the linear relationship between each variables:
```{r}
cor(birthweight)
```

By looking at the correlation matrix of the full data, first we can find that there is no relationship between pnumlbw and pnumsga with other variables, so we can delete these two variables from the dataset.

```{r}
birthweight_df =
  birthweight_df %>% 
  select(-pnumlbw, -pnumsga)
```


Then we focus on the relationship between the outcome "bwt" and other variables, we can find that there is high positive linear relationship between "bwt" and "bhead", "blength", and there is some small linear relationship between "bwt" and "gaweeks". 

So in our model, we first use "bhead" and "blength" to be the two main predictors only.


**Propose a regression model for birthweight**

```{r}
fit1 = lm(bwt ~ bhead + blength, data = birthweight_df)

summary(fit1)

fit1 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

```

From the results of the MLR of the these 2 covariates, through the globel F-test:

Since p-value< 2.2e-16, so we have enough evidence to reject the null and conclude that there is a regression relation between the outcome "bwt" and these 2 covariates.

We can also focus on the Adjusted $R^2$: 0.6812, it means that 68.12% of the variation in the outcome "bwt" is explained by linear association with the "bhead" and "blength".

In conclusion, this is not a bad model.


Make a plot of model residuals against fitted values:

```{r}
birthweight_df %>% 
  select(bwt, bhead, blength) %>% 
  modelr::add_residuals(fit1) %>% 
  modelr::add_predictions(fit1) %>% 
  ggplot(aes(x = resid, y = pred, color = bwt)) + geom_point()
```


We can also use bootstrap to simulate and drawing repeatedly from the original population.

```{r}
birthweight_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~ lm(bwt ~ bhead + blength, data = .x)),
         results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest() %>% 
  group_by(term) %>% 
  summarize(boot_estimate = mean(estimate),
            boot_se = sd(estimate)) %>% 
  knitr::kable(digits = 3)

```

The results we get from bootstrap is almost the same as what we have had.


**Compare the model to two others**

```{r}
fit1 = lm(bwt ~ bhead + blength, data = birthweight_df)
fit2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
fit3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + 
            bhead * babysex + blength * babysex + 
            bhead * blength * babysex, data = birthweight_df)
```

Make this comparison in terms of the cross-validated prediction error:

Fit models from training data and obtain corresponding RMSEs for the testing data for these three models.
```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(fit1 = map(train, ~lm(bwt ~ bhead + blength, data = .x)),
         fit2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         fit3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + 
                                 bhead * babysex + blength * babysex + 
                                 bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_fit1 = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
         rmse_fit2 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)),
         rmse_fit3 = map2_dbl(fit3, test, ~rmse(model = .x, data = .y)))
```

Plot the prediction error distribution for each model to make the comparison more clearly:

```{r}
cv_df %>% 
  select(.id, starts_with("rmse")) %>% 
  gather(key = model, value = rmse, rmse_fit1:rmse_fit3) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

From the plot above, we can find that the prediction errors of the model I built (using head circumference, length as main predictor only) and the third model which use head circumference, length, sex, and all interactions (including the three-way interaction) between these are almost the same, which both have lower prediction errors than the second model (using length at birth and gestational age as predictors for main effects only).





